BACI of biomass change for VOCC source cells for all years

### 2019-09-30 analysis/VOCC/4-vocc-BACI-multiyear.Rmd
revise for auto-render with params

---
title: "BACI of biomass change for VOCC source cells for all years"
author: "Philina English"
date: '2019-08-24'
output: html_document
---

Modified to allow thresholds chosen to vary by maturity class. 
Therefore need to run this file separately for each species-class combination.

Should matches be selected based on exact depth categories in addition to density (all within time periods)?

What does it mean for the analysis that the depth range at which VOCC occur within a species temperature range varies dramatically between time periods?

@@

#### Set species
```{r echo=TRUE}

#### Set age class
```{r echo=TRUE}
age <- "mature" # or mostly so
age <- "imm" 
```

#### Set vector type
```{r echo=TRUE}
global_only <- TRUE
biomass_threshold <- "75"

# biomass_threshold <- "50" # filter for climate values predicted to support 50% of max biomass 
#  biomass_threshold <- "25" # filter for climate values predicted to support 25% of max biomass... doesn't work for DO

climate <- "temperature"
 temp_threshold <- c(0.25)
# temp_threshold <- c(0.5)
# temp_threshold <- c(0.75)
# temp_threshold <- c(1)

 # climate <- "do"
 # do_threshold <- c(0.25)
# do_threshold <- c(0.5)

# climate <- "do and temperature"
```

#### Set Region 
```{r echo=TRUE}
# region <- "West Coast Vancouver Island"
region <- "both odd year surveys"
# region <- "West Coast Haida Gwaii"
```

#### Set default cell sizes and scale
```{r, echo=FALSE}
input_cell_size <- 2
dist_intercept <- input_cell_size/2
scale_fac <- 1
delta_t_step <- 2
skip_time <- NULL
```

```{r, include=FALSE}
library(dplyr)
library(ggplot2)
library(gfplot)
# library(gfdata)
library(sdmTMB)
# library(itsadug)
library(gfranges)
```

@@

```{r, message=FALSE, warning=FALSE, include=FALSE}
if (region == "both odd year surveys") {
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")
  start_years <- list("2009"=2009, "2011"=2011, "2013"=2013, "2015"=2015) 
  # maybe remove 2011 & 2015 once we can add "2017"=2017?
  years <- NULL
}

@@

params <- readRDS(paste0("data/root-values-by-species-by-age.rds"))

params <- params %>% mutate(model_type = ifelse(grepl("total", model), "total", "split"))

if (age == "imm") {
  params <- filter(params, age == "imm")
} else {
  params <- filter(params, age != "imm")
  if (any(params$model_type == "split")) { params <- filter(params, model_type != "total") }
}

params <- params[params$species == species, ] 
glimpse(params)

if (global_only) {
 params <- params %>% mutate(global = ifelse(grepl("_", model), "F", "T"))
 params <- filter(params, global == "T")
} else {
 if (model_ssid == 4) {
   params <- params %>% mutate(survey4 = ifelse(grepl("4", model), "T", "F"))
   params <- filter(params, survey4 == "T")
 }
}

if (climate == "temperature") {
  # optimal_temps <- params[rev(order(params$t_maxy)), ]$optimal_temp
  # optimal_temps <- na.omit(optimal_temps)
  # optimal_temp <- round(optimal_temps[1], digits = 2)
  # optimal_values <- optimal_temp

  if (biomass_threshold == "50") {
  .upper <- params[rev(order(params$t_maxy)), ]$upper_t_50 }
  if (biomass_threshold == "25") {
  .upper <- params[rev(order(params$t_maxy)), ]$upper_t_25 }
  .upper <- na.omit(.upper)

  upper_thresholds <- round(.upper[1], digits = 2)
  upper_model <- params[rev(order(params$t_maxy)), ]$model

@@

if (climate == "do") {
  # optimal_dos <- params[rev(order(params$do_maxy)), ]$optimal_do
  # optimal_dos <- na.omit(optimal_dos)
  # optimal_do <- round(optimal_dos[1], digits = 2)
  # optimal_values <- optimal_do
  params <- filter(params, lower_do_25 > 0.4)

  if (biomass_threshold == "50") {
  .lower <- params[rev(order(params$do_maxy)), ]$lower_do_50 }
  if (biomass_threshold == "25") {
  .lower <- params[rev(order(params$do_maxy)), ]$lower_do_25 }

  .lower <- na.omit(.lower)
  lower_thresholds <- round(.lower[1], digits = 2)
  lower_model <- params[rev(order(params$do_maxy)), ]$model
  upper_thresholds <- NA
  upper_model <- NULL
  variable_names <- c("do_est")

@@

if (climate == "do and temperature") {

  # optimal_dos <- params[rev(order(params$do_maxy)), ]$optimal_do
  # optimal_dos <- na.omit(optimal_dos)
  # optimal_do <- round(optimal_dos[1], digits = 2)
  # optimal_values <- optimal_do

  params <- filter(params, lower_do_25 > 0.5)
  if (biomass_threshold == "50") {
  .lower <- params[rev(order(params$do_maxy)), ]$lower_do_50 }
  if (biomass_threshold == "25") {
  .lower <- params[rev(order(params$do_maxy)), ]$lower_do_25 }
  .lower <- na.omit(.lower)
  lower_thresholds <- round(.lower[1], digits = 2)

  # optimal_temps <- params[rev(order(params$t_maxy)), ]$optimal_temp
  # optimal_temps <- na.omit(optimal_temps)
  # optimal_temp <- round(optimal_temps[1], digits = 2)
  # optimal_values <- optimal_temp

  if (biomass_threshold == "50") {
  .upper <- params[rev(order(params$t_maxy)), ]$upper_t_50 }
  if (biomass_threshold == "25") {
  .upper <- params[rev(order(params$t_maxy)), ]$upper_t_25 }
  .upper <- na.omit(.upper)
  upper_thresholds <- round(.upper[1], digits = 2)

  variable_names <- c("do_est", "temp")
  lower_thresholds <- c(lower_thresholds, NA)
  upper_thresholds <- c(NA, upper_thresholds)
  lower_change <- c(do_threshold, Inf)
  upper_change <- c(Inf, temp_threshold)
  upper_model <- params[rev(order(params$t_maxy)), ]$model
  lower_model <- params[rev(order(params$do_maxy)), ]$model

@@

glimpse(params)
```

# Calculate climate vectors
```{r}
rm(vocc)

vocc_by_year <- lapply(start_years, function(start_time) {

@@

  saveRDS(vocc, file = paste0(
    "data/vocc-", ssid_string, "-", climate_string, "-",
    min_string, "to", max_string, "-", start_time, "-", delta_t_total, ".rds"
  ))
}
 vocc
})  
# glimpse(vocc)
```

@@

### Filter vectors to match optimal range for chosen species
```{r}
trimmed_vectors <- lapply(vocc_by_year, function(vocc) {    
#start_time <- vocc$start_time[1]

@@

```{r}
png(
  file = paste0("figs/", spp,
    "/vocc-", min_string, "to", max_string, "-", 
    climate_string, "-", spp, "-", age, "-", ssid_string, "-perc_", biomass_threshold, "-", optimal_string, "-allpairs.png"
  ),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = trimmed_vector_plots,
  ncol = 2,
  top = grid::textGrob(paste("Vectors for cells exceeding", climate, "threshold of", optimal_string, "\n based on", biomass_threshold, "percent of maximum predicted", species, "biomass (", trim_models, ")"), gp=grid::gpar(fontsize=16))
)
dev.off()
```

@@

Get all biomass predictions 
```{r, echo=FALSE, warning=FALSE, error=FALSE, message=F}
priors <- FALSE
# covariates <- "+muddy+any_rock"
# covs <- gsub("\\+", "-", covariates)
covs <- gsub("\\+", "-", "-trawled+ssid")

rm(biomass_predictions)

if (age == "imm") {
  try({
  biomass_predictions <- readRDS(paste0(
    "data/", spp,
    "/all-predictions-", spp, covs, "-imm-biomass-prior-", priors, ".rds"
  ))
})
} else {
try({
  biomass_predictions <- readRDS(paste0(
    "data/", spp,
    "/all-predictions-", spp, covs, "-mat-biomass-prior-", priors, ".rds"
  ))
})
if (!exists("biomass_predictions")) {
try({
  biomass_predictions <- readRDS(paste0(
    "data/", spp,
    "/all-predictions-", spp, covs, "-total-biomass-prior-", priors, ".rds"
  ))
})
}
}
```

@@

  alldata
#})
```

```{r eval=FALSE, include=FALSE, echo=FALSE}
# lapply(alldata, function(i){ggplot(i, aes(x=cell_type, y=log(start_density))) + geom_boxplot()+facet_wrap(~start_time)})
```

@@

```{r}
rm(vocc_by_sp)
# try({
#   vocc_by_sp <- readRDS(paste0(
#     "data/BACI-", species, "-", age, "-", ssid_string, "-", climate_string, "-", optimal_string, "-", min_string, "to", max_string, "-multiyear-all.rds"
#   ))
# })

@@

if (!exists("vocc_by_sp")){
# matched <- lapply(alldata, function(alldata) {

  ## trim non-overlapping values to reduce size of dataset 
  control_min <- quantile(alldata$start_density[alldata$treat=="0"], 0.01)
  source_min <- quantile(alldata$start_density[alldata$treat=="1"], 0.01)
  # control_max <- quantile(alldata$start_density[alldata$treat=="0"], 1)
  # source_max <- quantile(alldata$start_density[alldata$treat=="1"], 1)

@@

  # # Using exact match and rounding
  # # Choose data order if not using random
  # alldata <- alldata[(order(alldata$y)), ]
  # if (order == "increasing") alldata <- alldata[rev(order(alldata$start_density)), ]
  # if (order == "decreasing") alldata <- alldata[rev(order(alldata$start_density)), ]

  matched <- MatchIt::matchit(as.formula(match_formula), 
    exact = c("start_density.st", "start_time"),
    method = "nearest", m.order = "random",
    distance = "probit",
    discard = "both",
    data = alldata)
  # matched
# })
}
```

@@

n <- nrow(vocc_by_sp[[1]])
species <- rep(species, n) 
mature <- rep(age, n)
data <- vocc_by_sp[[1]]
class <- cbind(species, mature)
df <- cbind(class, data)
species <- species[[1]]

@@

if (climate=="temperature") dir.create(file.path("data/_all", climate_string, biomass_threshold_string, max_string))

if (climate=="temperature") {
  saveRDS(df, file = paste0(
    "data/_all/", climate_string,"/", "perc_", biomass_threshold,"/", max_string,"/vocc-", climate_string, "-", 
     max_string, "-", spp, "-", age, "-", optimal_string, "-", ssid_string, "-all.rds"
  ))
}

if (climate=="do") {
  dir.create(file.path("data/_all", climate_string))  
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string))  
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string, min_string))  
  }
if (climate=="do") {
  saveRDS(df, file = paste0(
    "data/_all/", climate_string,"/", "perc_", biomass_threshold,"/", min_string,"/vocc-", climate_string, "-",
    min_string, "to", max_string, "-", spp, "-", age, "-", optimal_string, "-", ssid_string, "-all.rds"
  ))
}

if (climate=="do and temperature") {
  dir.create(file.path("data/_all", climate_string))  
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string))  
}

if (climate=="do and temperature") {
  saveRDS(df, file = paste0(
    "data/_all/", climate_string, "/", "perc_", biomass_threshold,"/vocc-", climate_string, "-",
    min_string, "to", max_string, "-", spp, "-", age, "-", optimal_string, "-", ssid_string, "-all.rds"
  ))
}

# View(df)
```

@@

```{r}
png(
  file = paste0("figs/", spp,
    "/matches-", min_string, "to", max_string, "-",
    climate_string, "-", spp, "-", age, "-", ssid_string, "-",
    climate_string, "-perc_", biomass_threshold, "-", optimal_string, "-allpairs1.png"
  ),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  p1,p2,p3,p4,p5,
  ncol = 2,
  top = grid::textGrob(paste("Matched pairs for", climate, "threshold of", optimal_string, "\n based on", biomass_threshold, "percent of maximum predicted", species, "biomass"), gp=grid::gpar(fontsize=16))
)
dev.off()
```

### Basic BACI
```{r eval=F}
for (j in (variable_names)) {
  baci_formula <- paste0("log_density~after + cell_type + after:cell_type + n_targets + vect_dist + vect_dist2 + std_", j, "+ std_", j, "2 + (1|icell) + (1|matchobs) + (1|start_time)")
}

m <- lmerTest::lmer(as.formula(baci_formula), data=data)
summary(m)
```

```{r eval=F}
sjPlot::plot_model(m, type = "std2", order.terms=c(1,2,8,3,4,5,6,7), title = paste(species, "adult"))
```

### GAMM
```{r eval=F}
 gamm_formula <- paste0("log_density ~ ", 
  # "time * start_time + ",
  #"start_time * cell_type + ",
  "time * cell_type  + s(std_log_depth) + s(X,Y) ") #+ s(vect_dist)

# for (j in (variable_names)) {
#  gamm_formula <- paste0(gamm_formula, "+ s(std_", j, ")")
#  }

gam4 <- gamm4::gamm4(as.formula(gamm_formula), 
  random = ~(1|matchobs) + (1|icell) 
  # + (1|start_time)
  + (time|start_time) 
  # + (cell_type|start_time)
  , data=data)

summary(gam4$gam)

plot(gam4$gam,pages=1)
```

```{r, eval=FALSE, results="hide", include=FALSE}
plot_parametric(gam4$gam, pred=list(time=c("begin","end"), cell_type=c("control", "source"), start_time=c("2009","2011","2013","2015")), parametricOnly = TRUE, main="", xlab ="log_density"
  #, groups = cell_type, gcolor = my_cols, color = my_cols["time"]
  ) 
```

```{r}
spp
```

>>>>

---
title: "BACI of biomass change for VOCC source cells for all years"
author: "Philina English"
date: '2019-08-24'
output: html_document
params: 
    species: "Yelloweye Rockfish" 
    region: "West Coast Vancouver Island"
    age: "mature"
    biomass_threshold: "25"
    climate: "do"
    threshold: c(0.25) 
---

@@

```{r pkgs, cache=FALSE, warning=FALSE, message=FALSE}
library("dplyr")
library("ggplot2")
library("gfplot")
library("sdmTMB")
library("gfranges")
```

#### Set parameters
```{r echo=TRUE}
species <- params$species
age <- params$age
region <- params$region
biomass_threshold <- params$biomass_threshold
climate <- params$climate
```

#### Set default cell sizes and scale
```{r, echo=FALSE}
global_only <- TRUE
input_cell_size <- 2
dist_intercept <- input_cell_size/2
scale_fac <- 1
delta_t_step <- 2
skip_time <- NULL
```

@@

```{r, message=FALSE, warning=FALSE, include=FALSE}
if (region == "both odd year surveys") {
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")
  start_years <- list("2009"=2009, "2011"=2011, "2013"=2013, "2015"=2015) 
  # maybe remove 2011 & 2015 once we can add "2017"=2017 to avoid start and end values overlapping
  years <- NULL
}

@@

root_params <- readRDS(paste0("data/root-values-by-species-by-age.rds"))

root_params <- root_params %>% mutate(model_type = ifelse(grepl("total", model), "total", "split"))

if (age == "imm") {
  root_params <- filter(root_params, age == "imm")
} else {
  root_params <- filter(root_params, age != "imm")
  if (any(root_params$model_type == "split")) { root_params <- filter(root_params, model_type != "total") }
}

root_params <- root_params[root_params$species == species, ] 
glimpse(root_params)

if (global_only) {
 root_params <- root_params %>% mutate(global = ifelse(grepl("_", model), "F", "T"))
 root_params <- filter(root_params, global == "T")
} else {
 if (model_ssid == 4) {
   root_params <- root_params %>% mutate(survey4 = ifelse(grepl("4", model), "T", "F"))
   root_params <- filter(root_params, survey4 == "T")
 }
}

if (climate == "temperature") {

temp_threshold <- params$threshold

  if (biomass_threshold == "75") {
  .lower <- root_params[rev(order(root_params$do_maxy)), ]$upper_t_75 }
  if (biomass_threshold == "50") {
  .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_50 }
  if (biomass_threshold == "25") {
  .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_25 }
  .upper <- na.omit(.upper)

  upper_thresholds <- round(.upper[1], digits = 2)
   if (is.na(upper_thresholds)) {stop(print("Temp maximum not modelled"))}

  upper_model <- root_params[rev(order(root_params$t_maxy)), ]$model

@@

if (climate == "do") {
  do_threshold <- params$threshold
  root_params <- filter(root_params, lower_do_25 > 0.4)

  if (biomass_threshold == "75") {
  .lower <- root_params[rev(order(root_params$do_maxy)), ]$lower_do_75 }
  if (biomass_threshold == "50") {
  .lower <- root_params[rev(order(root_params$do_maxy)), ]$lower_do_50 }
  if (biomass_threshold == "25") {
  .lower <- root_params[rev(order(root_params$do_maxy)), ]$lower_do_25 }

  .lower <- na.omit(.lower)
  lower_thresholds <- round(.lower[1], digits = 2)
  if (is.na(lower_thresholds)) {stop(print("DO minimum not modelled"))}
  lower_model <- root_params[rev(order(root_params$do_maxy)), ]$model

  upper_thresholds <- NA
  upper_model <- NULL
  variable_names <- c("do_est")

@@

if (climate == "do and temperature") {
  temp_threshold <- params$threshold
  do_threshold <- params$threshold

  root_params <- filter(root_params, lower_do_25 > 0.5)
  if (biomass_threshold == "75") {
  .lower <- root_params[rev(order(root_params$do_maxy)), ]$lower_do_75 }
  if (biomass_threshold == "50") {
  .lower <- root_params[rev(order(root_params$do_maxy)), ]$lower_do_50 }
  if (biomass_threshold == "25") {
  .lower <- root_params[rev(order(root_params$do_maxy)), ]$lower_do_25 }
  .lower <- na.omit(.lower)
  lower_thresholds <- round(.lower[1], digits = 2)

  if (biomass_threshold == "75") {
  .lower <- root_params[rev(order(root_params$do_maxy)), ]$upper_t_75 }
  if (biomass_threshold == "50") {
  .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_50 }
  if (biomass_threshold == "25") {
  .upper <- root_params[rev(order(root_params$t_maxy)), ]$upper_t_25 }
  .upper <- na.omit(.upper)
  upper_thresholds <- round(.upper[1], digits = 2)

  variable_names <- c("do_est", "temp")
  lower_thresholds <- c(lower_thresholds, NA)
  upper_thresholds <- c(NA, upper_thresholds)
  lower_change <- c(do_threshold, Inf)
  upper_change <- c(Inf, temp_threshold)
  upper_model <- root_params[rev(order(root_params$t_maxy)), ]$model
  lower_model <- root_params[rev(order(root_params$do_maxy)), ]$model

@@

glimpse(root_params)
```

# Calculate climate vectors
```{r}
vocc_by_year <- lapply(start_years, function(start_time) {

@@

  saveRDS(vocc, file = paste0(
    "data/vocc-", ssid_string, "-", climate_string, "-",
    min_string, "to", max_string, "-", start_time, "-", delta_t_total, ".rds"
  ))
}
 vocc
})  
```

@@

### Filter vectors to match optimal range for chosen species
```{r}
trimmed_vectors <- lapply(vocc_by_year, function(vocc) {

@@

```{r}
png(
  file = paste0("figs/", spp,
    "/vocc-", min_string, "to", max_string, "-", 
    climate_string, "-", spp, "-", age, "-", ssid_string, "-perc_", biomass_threshold, "-", optimal_string, "-allpairs-test.png"
  ),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = trimmed_vector_plots,
  ncol = 2,
  top = grid::textGrob(paste("Vectors for cells exceeding", climate, "threshold of", optimal_string, "\n based on", biomass_threshold, "percent of maximum predicted", species, "biomass (", trim_models, ")"), gp=grid::gpar(fontsize=16))
)
dev.off()
```

@@

Get all biomass predictions 
```{r echo=FALSE, warning=FALSE}
priors <- FALSE
covs <- "-trawled-ssid"

if (age == "imm") {
  biomass_predictions <- readRDS(paste0(
    "data/", spp, "/all-predictions-", spp, covs, 
    "-imm-biomass-prior-", priors, ".rds"))
}

if (age == "mature") {
  biomass_predictions <- readRDS(paste0(
    "data/", spp, "/all-predictions-", spp, covs, 
    "-mat-biomass-prior-", priors, ".rds"))
}
```

@@

 # alldata
#})
```

@@

```{r}
#rm(vocc_by_sp)
# try({
#   vocc_by_sp <- readRDS(paste0(
#     "data/BACI-", species, "-", age, "-", ssid_string, "-", climate_string, "-", optimal_string, "-", min_string, "to", max_string, "-multiyear-all.rds"
#   ))
# })

@@

if (!exists("vocc_by_sp")){
# matched <- lapply(alldata, function(alldata) {  
  ## trim non-overlapping values to reduce size of dataset 
  control_min <- quantile(alldata$start_density[alldata$treat=="0"], 0.01)
  source_min <- quantile(alldata$start_density[alldata$treat=="1"], 0.01)
  # control_max <- quantile(alldata$start_density[alldata$treat=="0"], 1)
  # source_max <- quantile(alldata$start_density[alldata$treat=="1"], 1)

@@

  # # Using exact match and rounding
  # # Choose data order if not using random
  # alldata <- alldata[(order(alldata$y)), ]
  # if (order == "increasing") alldata <- alldata[rev(order(alldata$start_density)), ]
  # if (order == "decreasing") alldata <- alldata[rev(order(alldata$start_density)), ]
# set.seed(99999)
  matched <- MatchIt::matchit(as.formula(match_formula), 
    exact = c("start_density.st", "start_time"),
    method = "nearest", m.order = "random",
    distance = "probit",
    discard = "both",
    data = alldata)
  # matched
# })
}
```

@@

n <- nrow(vocc_by_sp[[1]])
species <- rep(species, n) 
mature <- rep(age, n)
ssid <- rep(ssid_string, n)
data <- vocc_by_sp[[1]]
df<- cbind(species, mature, ssid, data)
species <- species[[1]]

@@

if (climate=="temperature") {
dir.create(file.path("data/_all", climate_string, biomass_threshold_string, max_string))
dir.create(file.path("data/_all", climate_string, biomass_threshold_string, max_string, age))
}
if (climate=="temperature") {
  saveRDS(df, file = paste0("data/_all/", climate_string,"/", "perc_", biomass_threshold,"/", max_string,"/", age, "/vocc-", climate_string, "-", max_string, "-", spp, "-", age, "-", optimal_string, "-", ssid_string, "-all.rds"
  ))
}

if (climate=="do") {
  dir.create(file.path("data/_all", climate_string))  
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string))  
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string, min_string))
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string, min_string, age))  
  }
if (climate=="do") {
  saveRDS(df, file = paste0("data/_all/", climate_string,"/", "perc_", biomass_threshold,"/", min_string,"/", age, "/vocc-", climate_string, "-", min_string, "to", max_string, "-", spp, "-", age, "-", optimal_string, "-", ssid_string, "-all.rds"
  ))
}

if (climate=="do and temperature") {
  dir.create(file.path("data/_all", climate_string))  
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string))  
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string, age))  
}

if (climate=="do and temperature") {
  saveRDS(df, file = paste0("data/_all/", climate_string, "/", "perc_", biomass_threshold,"/", age, "/vocc-", climate_string, "-", min_string, "to", max_string, "-", spp, "-", age, "-", optimal_string, "-", ssid_string, "-all.rds"
  ))
}
```

@@

```{r}
png(
  file = paste0("figs/", spp,
    "/matches-", min_string, "to", max_string, "-",
    climate_string, "-", spp, "-", age, "-", ssid_string, "-",
    climate_string, "-perc_", biomass_threshold, "-", optimal_string, ".png"
  ),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  p1,p2,p3,p4,p5,
  ncol = 2,
  top = grid::textGrob(paste("Matched pairs for", climate, "threshold of", optimal_string, "\n based on", biomass_threshold, "percent of maximum predicted", species, "biomass"), gp=grid::gpar(fontsize=16))
)
dev.off()
```
